\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-09 paper/queries.tex
paper-fix: modified queries so that they actually work with simpledb

\newcounter{queryno}
\begin{tabular}{cl}
\toprule
\# & \multicolumn{1}{c}{Query} \\
\midrule
1 & \verb|SELECT income, AVG(weight) FROM demo, exams WHERE demo.id = exams.id id GROUP BY income;| \refstepcounter{queryno} \label{q1} \\
2 & 
\begin{minipage}{6in}
\begin{lstlisting}[breaklines]
SELECT income, COUNT(*), AVG(cholesterol) 
FROM demo, exams, labs WHERE demos.id = exams.id AND exams.id = labs.id AND
income = 15 OR income = 13 AND weight >= 63 GROUP BY income;
\end{lstlisting}
\end{minipage}
\refstepcounter{queryno} \label{q2} \\
3 & \verb|SELECT MAX(blood_lead) FROM exams, labs WHERE exams.id = labs.id AND waist_circumference >= 87;| \refstepcounter{queryno} \label{q3} \\
% 1 & \verb|SELECT BLD FROM acs;| \refstepcounter{queryno} \label{q1} \\
% 2 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \refstepcounter{queryno} \label{q2} \\
% 3 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \refstepcounter{queryno} \label{q3} \\
% 4 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \refstepcounter{queryno} \label{q4} \\
% 5 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \refstepcounter{queryno} \label{q5} \\
% 6 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \refstepcounter{queryno} \label{q6} \\
% 7 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \refstepcounter{queryno} \label{q7} \\
% 8 & \verb|SELECT MIN(RMSP) as min_num_rooms FROM acs WHERE RWAT=2;| \refstepcounter{queryno} \label{q8} \\
% 9 & \verb|SELECT * FROM dirty m where m.f1 >= 2;| \refstepcounter{queryno} \label{q9} \\
% 10 & \verb|SELECT * FROM dirty where dirty.f1 <= 2;| \refstepcounter{queryno} \label{q10} \\
% 11 & \verb|SELECT MAX(f2) as max_f2 FROM dirty GROUP BY dirty.f1;| \refstepcounter{queryno} \label{q11} \\
% 12 & \verb|SELECT m1.f1, m1.f2 FROM dirty m1, clean m2 WHERE m1.f1 = m2.f1 and m1.f1 = 1 and m2.f2 = 69;| \refstepcounter{queryno} \label{q12} \\
% 13 & \verb|SELECT d1.f1 FROM dirty d1, clean d2 WHERE d1.f1 = d2.f1 and d2.f2 = 50;| \refstepcounter{queryno} \label{q13} \\
\bottomrule
\end{tabular}

>>>>

\newcounter{queryno}
\begin{tabular}{cl}
\toprule
\# & \multicolumn{1}{c}{Query} \\
\midrule
1 & \verb|SELECT income, AVG(weight) FROM demo, exams WHERE demo.id = exams.id GROUP BY income;| \refstepcounter{queryno} \label{q1} \\
2 & 
\begin{minipage}{6in}
\begin{lstlisting}[breaklines]
SELECT income, AVG(cholesterol) 
FROM demo, exams, labs WHERE demo.id = exams.id AND exams.id = labs.id AND
income <= 15 AND income >= 13 AND weight >= 63 GROUP BY income;
\end{lstlisting}
\end{minipage}
\refstepcounter{queryno} \label{q2} \\
3 & \verb|SELECT MAX(blood_lead) FROM exams, labs WHERE exams.id = labs.id AND waist_circumference >= 87;| \refstepcounter{queryno} \label{q3} \\
% 1 & \verb|SELECT BLD FROM acs;| \refstepcounter{queryno} \label{q1} \\
% 2 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \refstepcounter{queryno} \label{q2} \\
% 3 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \refstepcounter{queryno} \label{q3} \\
% 4 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \refstepcounter{queryno} \label{q4} \\
% 5 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \refstepcounter{queryno} \label{q5} \\
% 6 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \refstepcounter{queryno} \label{q6} \\
% 7 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \refstepcounter{queryno} \label{q7} \\
% 8 & \verb|SELECT MIN(RMSP) as min_num_rooms FROM acs WHERE RWAT=2;| \refstepcounter{queryno} \label{q8} \\
% 9 & \verb|SELECT * FROM dirty m where m.f1 >= 2;| \refstepcounter{queryno} \label{q9} \\
% 10 & \verb|SELECT * FROM dirty where dirty.f1 <= 2;| \refstepcounter{queryno} \label{q10} \\
% 11 & \verb|SELECT MAX(f2) as max_f2 FROM dirty GROUP BY dirty.f1;| \refstepcounter{queryno} \label{q11} \\
% 12 & \verb|SELECT m1.f1, m1.f2 FROM dirty m1, clean m2 WHERE m1.f1 = m2.f1 and m1.f1 = 1 and m2.f2 = 69;| \refstepcounter{queryno} \label{q12} \\
% 13 & \verb|SELECT d1.f1 FROM dirty d1, clean d2 WHERE d1.f1 = d2.f1 and d2.f2 = 50;| \refstepcounter{queryno} \label{q13} \\
\bottomrule
\end{tabular}
